Deep Probabilistic Models for Camera Geo-Calibration

### 2018-10-24 chapters/fasthorizon/paper.tex
last change

In this chapter, we will develop a constraint function for
camera pose. Since the camera roll and pitch angle can be derived from
the horizon line position, our algorithm focuses on detecting the
horizon line from the input image.

>>>>

In this chapter, we develop a constraint function for the
camera pose. Since the camera roll and pitch angles can be derived from
the horizon line position, our algorithm focuses on detecting the
horizon line from the input image.
